### 2011-06-01 thesis/contents.tex
Spplited Introduction and Semantic Mpaping chapter out of contents.tex

\chapter{Introduction}
% Introduce:
%  Mobile Robotics, A.I.
%  Interaction with Humans
%  Need for concepts/semantic information
%  Dynamic human environment
%  Non-feasibility of hard-coded concepts
%  Requirements to detect novelty and handle it.
For a long time humanity has fantasized that one day robots will walk among us.
They will move and be able to interact with us. Understand our concepts and
be able to reason.

They need to possess ability to adapt to situations as its infeasible to rely
on extensive man-work to tag objects, map space and code all the aspects that
make up our human-reality.

% == Introduce the need of semantic representations ==
%
% There is a lot of low-level methods (or specific knowledge to robots)
% But the creation of semantic representations allow to bridge that low-level
% sensing with high-level concepts that facilitate several high-level Tasks.

% Importance of mapping and localization in a robot as well as reasoning on
% properties of each space.
% Humans give labels to space that characterized the properties and activities
% expected to be performed on them.
% Such information is of great interest to be structured and organized in such
% a way reasoning and planning can be implemented.
%
% It also holds an important role in long-term planning and stability as it
% hides the space-time local details and allows to focus on high-level thinking.

% Deal with uncertainty -> need for probabilistic models.
% Deal with semantic    -> need of structured models such as graphical models.

Example of what kind of an high-level thinking on space and its semantics can
provide: Get me a beer/milk concept.

% == Reasoning about need for Novelty Detection ==
%
% Dynamic environment (inability to know the environment or even to be possible
% to map all semantic concepts to interact with humans).
%
% Knowledge-Awareness (knowing what we know... And detecting novel cases)
% Identify gaps in the semantic knowledge.
% Automatic detection and learning of novel concepts.
%
% Increase robustness
% Self-Extending
%

\section{Problem and Goals}
% Extend a probabilistic graphical modelling framework with capabilities to
% detect novelty.
% Both in terms of novel classes as of novel structure.
%
Given a probabilistic structure representing the sensed conceptual knowledge
obtained by the agent develop methods able to detect novelty present
either on new semantic concepts (new classes) or even on structure that was
previously unknown.

% Yeah thats what you call dream :P
In an extreme ideal case the agent should be able to go from zero-knowledge to
understanding presence of certain objects (as generators of a set of sensed
sensed properties grouped locally), understand areas within rooms (sink-area on
on a kitchen), rooms as separated by doors, and understand environments such
as office, home, warehouse, spaceship.

For that the probabilistic semantic representation presented by
\cite{andrzej2011phd} is used.

% If everything goes fine... 2 of the "Future Directions" proposed are 
% Novelty Detection and Learning of Novel Concepts:
%  Identify Gaps in Spatial and Semantic Knowledge -> Addressed
%  Performing learning of new concepts -> Outside Scope / No Time
%
% Using Properties for Space Segmentation
%  If we move on detecting novel structures on the graph we are addressing this
%  issue.

\section{Thesis Outline}
The rest of this thesis is structured as follows:

\autoref{chap:background} introduces background concepts for understanding the
presented thesis. In particular \autoref{sec:graphical-models} introduces
\emph{probabilistic graphical models} that lay the base modelling tool for
the used structured semantic representation.

\autoref{chap:semantic-mapping} describes the system proposed by
\cite{andrzej}. In special it introduces the \emph{conceptual map} of the system
that is responsible for the creation of the \emph{probabilistic semantic
representation} that this thesis aims at improving by developing methods with
the capability to identify knowledge gaps.

\autoref{chap:novelty-intro} introduces novelty detection under a
statistical view point and how to interpret it as a threshold function.
A simple approach on how to perform novelty on very simple graphs
is given together with some results on the impact of using semi-supervised
novelty detection to improve the system performance.

\autoref{chap:novelty} presents the developed techniques developed to identify
novelty on the semantic representation.

\autoref{chap:conclusions} draws conclusions on the developed work and presents
interesting directions for future works.

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\chapter{Semantic Mapping}\label{chap:semantic-mapping}

% Advantages of Multi-modal approaches
%

\section{Dora Architecture Overview}
\subsection{System organization}
\subsubsection{Sensory Layer}
\subsubsection{Categorical Layer}
\subsubsection{Place Layer}
\subsubsection{Conceptual Layer}

\section{Features}

\section{Conceptual Knowledge}
\section{Conceptual Map}
\label{sec:clues-from-low-level}

>>>>

\input{introduction}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\input{semantic-mapping}

### 2011-06-01 thesis/introduction.tex
Spplited Introduction and Semantic Mpaping chapter out of contents.tex

\chapter{Introduction} \label{chap:intro}

\section*{}

AO primeiro capítulo da dissertação deve servir para apresentar o
enquadramento e a moti\-va\-ção do trabalho e para identificar e
definir os problemas que a dissertação aborda.
Deve resumir as metodologias utilizadas no trabalho e termina
apresentando um breve resumo de cada um dos capítulos
posteriores.

Este documento ilustra o formato a usar em dissertações na \gls{FEUP}, não
servindo de exemplo sobre os conteúdos a usar.
São dados exemplos de margens, cabeçalhos, títulos, paginação, estilos
de índices, etc. 
São ainda dados exemplos de formatação de citações, figuras e tabelas,
equações, referências cruzadas, lista de referências e índices.

Uma recolha de normas existentes sobre este assunto pode ser
encontrada em~\cite{kn:Mat93}.

\begin{quote}
  ``Like the Abstract, the Introduction should be written to engage the
  interest of the reader. It should also give the reader an idea of
  how the dissertation is structured, and in doing so, define the
  thread of the contents.''~\cite{kn:Tha01} 
\end{quote}

Blabla \gls{Kinect}

\section{Context} \label{sec:context}

Esta secção descreve a área em que o trabalho se insere, podendo
referir um eventual projecto de que faz parte e apresentar uma breve
descrição da empresa onde o trabalho decorreu.

\section{Motivation and Goals} \label{sec:goals}

Apresenta a motivação e enumera os objectivos do trabalho terminando
com um resumo das metodologias para a prossecução dos objectivos.

\section{Thesis Outline} \label{sec:outline}

The rest of this thesis is structured as follows\dots

>>>>

\chapter{Introduction}
% Introduce:
%  Mobile Robotics, A.I.
%  Interaction with Humans
%  Need for concepts/semantic information
%  Dynamic human environment
%  Non-feasibility of hard-coded concepts
%  Requirements to detect novelty and handle it.
For a long time humanity has fantasized that one day robots will walk among us.
They will move and be able to interact with us. Understand our concepts and
be able to reason.

They need to possess ability to adapt to situations as its infeasible to rely
on extensive man-work to tag objects, map space and code all the aspects that
make up our human-reality.

% == Introduce the need of semantic representations ==
%
% There is a lot of low-level methods (or specific knowledge to robots)
% But the creation of semantic representations allow to bridge that low-level
% sensing with high-level concepts that facilitate several high-level Tasks.

% Importance of mapping and localization in a robot as well as reasoning on
% properties of each space.
% Humans give labels to space that characterized the properties and activities
% expected to be performed on them.
% Such information is of great interest to be structured and organized in such
% a way reasoning and planning can be implemented.
%
% It also holds an important role in long-term planning and stability as it
% hides the space-time local details and allows to focus on high-level thinking.

% Deal with uncertainty -> need for probabilistic models.
% Deal with semantic    -> need of structured models such as graphical models.

Example of what kind of an high-level thinking on space and its semantics can
provide: Get me a beer/milk concept.

% == Reasoning about need for Novelty Detection ==
%
% Dynamic environment (inability to know the environment or even to be possible
% to map all semantic concepts to interact with humans).
%
% Knowledge-Awareness (knowing what we know... And detecting novel cases)
% Identify gaps in the semantic knowledge.
% Automatic detection and learning of novel concepts.
%
% Increase robustness
% Self-Extending
%

\section{Problem and Goals}
% Extend a probabilistic graphical modelling framework with capabilities to
% detect novelty.
% Both in terms of novel classes as of novel structure.
%
Given a probabilistic structure representing the sensed conceptual knowledge
obtained by the agent develop methods able to detect novelty present
either on new semantic concepts (new classes) or even on structure that was
previously unknown.

% Yeah thats what you call dream :P
In an extreme ideal case the agent should be able to go from zero-knowledge to
understanding presence of certain objects (as generators of a set of sensed
sensed properties grouped locally), understand areas within rooms (sink-area on
on a kitchen), rooms as separated by doors, and understand environments such
as office, home, warehouse, spaceship.

For that the probabilistic semantic representation presented by
\cite{andrzej2011phd} is used.

% If everything goes fine... 2 of the "Future Directions" proposed are 
% Novelty Detection and Learning of Novel Concepts:
%  Identify Gaps in Spatial and Semantic Knowledge -> Addressed
%  Performing learning of new concepts -> Outside Scope / No Time
%
% Using Properties for Space Segmentation
%  If we move on detecting novel structures on the graph we are addressing this
%  issue.

\section{Thesis Outline}
The rest of this thesis is structured as follows:

\autoref{chap:background} introduces background concepts for understanding the
presented thesis. In particular \autoref{sec:graphical-models} introduces
\emph{probabilistic graphical models} that lay the base modelling tool for
the used structured semantic representation.

\autoref{chap:semantic-mapping} describes the system proposed by
\cite{andrzej}. In special it introduces the \emph{conceptual map} of the system
that is responsible for the creation of the \emph{probabilistic semantic
representation} that this thesis aims at improving by developing methods with
the capability to identify knowledge gaps.

\autoref{chap:novelty-intro} introduces novelty detection under a
statistical view point and how to interpret it as a threshold function.
A simple approach on how to perform novelty on very simple graphs
is given together with some results on the impact of using semi-supervised
novelty detection to improve the system performance.

\autoref{chap:novelty} presents the developed techniques developed to identify
novelty on the semantic representation.

\autoref{chap:conclusions} draws conclusions on the developed work and presents
interesting directions for future works.
